\LARGE \bf Steering a Swarm Using Global Inputs\\ and Swarm Statistics

### 2017-04-27 journalSwarmControl/Introduction.tex
All the comments are solved.

\begin{figure}
\centering
\begin{overpic}[width=\columnwidth]{MainExpFig.pdf}\end{overpic}
\caption{\label{fig:bigPictureMeanAndVarianceForSwarm} 
A swarm of particles, all controlled by a uniform control input, can be effectively controlled by a hybrid controller that knows only the mean and variance of the robot distribution.  
Here a swarm of particles (kilobot robots) pushes a green hexagon toward the goal (see video attachment).
}
\end{figure}

@@

 Our paper is organized as follows.  After a discussion of related work in \S \ref{sec:RelatedWork},  we describe our experimental methods for an online human-user experiment and their results in \S \ref{sec:expMethods}. Inspired by these results, we prove that the mean and variance of a particle swarm are controllable in \S \ref{sec:theory}, and present automatic controllers in \S \ref{sec:simulation}. We use these controllers as primitives and present a framework for manipulating an object through a maze in \S \ref{sec:exp}. 
 We conclude with implementations of these controllers in our hardware robots and use them to complete an object manipulation task with 100 kilobots in \S \ref{sec:realExperiment}.

>>>>

\begin{figure}
\centering
\begin{overpic}[width=\columnwidth]{MainExpFig.pdf}\end{overpic}
\caption{\label{fig:bigPictureMeanAndVarianceForSwarm} 
A swarm of particles, all actuated by a uniform control input where each particle gets the same control input, can be effectively manipulated by a control law that uses only the mean and variance of the robot distribution.  
Here a swarm of particles (kilobot robots) pushes a green hexagon toward the goal (see video attachment).
}
\end{figure}

@@

 Our paper is organized as follows.  After a discussion of related work in \S \ref{sec:RelatedWork},  we describe our experimental methods for an online human-user experiment and their results in \S \ref{sec:expMethods}. Next we prove that the mean and variance of a particle swarm are controllable in \S \ref{sec:theory}, and present automatic controllers in \S \ref{sec:simulation}. We use these controllers as primitives and present a framework for manipulating an object through a maze in \S \ref{sec:exp}. 
 We conclude with implementations of these controllers in our hardware robots and use them to complete an object manipulation task with 100 kilobots in \S \ref{sec:realExperiment}.

### 2017-04-27 journalSwarmControl/conclusion.tex
All the comments are solved.

    %Micro- and nanorobotics have the potential to revolutionize many applications including targeted material delivery, assembly, and surgery.  
  The small size of micro and nano particles makes individual control and autonomy challenging, so currently these particles are steered by global control inputs such as magnetic fields or chemical gradients. To investigate this control challenge, this paper introduced \href{http://www.swarmcontrol.net}{SwarmControl.net}, an open-source tool for large-scale user experiments where human users steer swarms of robots to accomplish tasks.  Analysis of the game play results revealed benefits of measuring and controlling statistics of the swarm rather than full state feedback.

Inspired by the three lessons from swarmcontrol.net, this paper designed controllers and controllability results using only the mean and variance of a particle swarm. 
We developed a hysteresis based controller to regulate the position and variance of a swarm. We designed a controller for object manipulation using policy iteration for path planning, regions for outlier rejection and potential fields for minimizing moving the object backwards. These controllers were used as primitives for an object manipulation task.
All automatic controllers were implemented using 100 kilobots steered by the direction of a global light source.
These experiments culminated in an object manipulation task in a workspace with obstacles.

@@

Our main goal is to perform assembly using particle swarms to manipulate and attach components. This task requires controlling the position and orientation of components, manipulate them through obstacles and other components, and apply force and torque to components. This work provides foundational algorithms and techniques for steering swarms, object manipulation, and addressing obstacle fields, but there are many opportunities to extend the work.

>>>>

    %Micro- and nanorobotics have the potential to revolutionize many applications including targeted material delivery, assembly, and surgery.  
  The small size of micro and nano particles makes individual control and autonomy challenging, so currently these particles are steered by global control inputs such as magnetic fields or chemical gradients. To investigate this control challenge, this paper introduced \href{http://www.swarmcontrol.net}{SwarmControl.net}, an open-source tool for large-scale user experiments where human users steer swarms of robots to accomplish tasks.  Analysis of the game play results revealed benefits of measuring and controlling statistics of the swarm rather than full state feedback, robustness to IID noise, and small effects of varying population size of large swarms.

Inspired by the three lessons from swarmcontrol.net, this paper designed controllers and controllability results using only the mean and variance of a particle swarm. 
We developed a hysteresis based controller to regulate the position and variance of a swarm. We designed a controller for object manipulation using policy iteration for path planning, regions for outlier rejection, and potential fields for minimizing moving the object backwards. 
All automatic controllers were implemented using 100 kilobots steered by the direction of a global light source.
These experiments culminated in an object manipulation task in a workspace with obstacles.

@@

Our future goal is to perform assembly using particle swarms to manipulate and attach components. This task requires controlling the position and orientation of components, manipulating them through obstacles and other components, and applying force and torque to components. This work provides foundational algorithms and techniques for steering swarms, object manipulation, and addressing obstacle fields, but there are many opportunities to extend the work.

### 2017-04-27 journalSwarmControl/expResults.tex
All the comments are solved.

We designed six experiments to investigate human control of large swarms for manipulation tasks.  Screenshots of representative experiment are shown in Fig.~\ref{fig:5experiments}.  Each experiment examined the effects of varying a single parameter: population of particles for manipulation, four levels of visual feedback, different levels of Brownian noise, position control with 1 to 10 particles, and three control architectures for both assembly and foraging tasks. The users could choose which experiment to try, and our architecture randomly assigned a parameter value for each trial.  We recorded the completion time and the participant ID for each successful trial.  
%As Fig.~\ref{fig:Learning} shows, one-third of all participants played only a single game.  Still, many played multiple games, and their decreasing completion times demonstrates their skills improved.

@@

%Transport of goods and materials between points is at the heart of all engineering and construction in real-world systems. 
This experiment varied from 1 to 500 the population of particles used to transport an object. The total area, maximum particle speed, and total net force the swarm could produce were constant. The particles pushed a large hexagonal object through an  {\sffamily S}-shaped maze. We hypothesized participants would complete the task faster with more particles. The results, shown in Fig.~\ref{fig:ResVaryNu}, do not support our hypothesis, indicating a minimum around 130 particles.

@@

Our hypothesis predicted a steady decay in performance as the amount of visual feedback decreased.
Our experiment indicated the opposite: players with just the mean completed the task faster than those with full-state feedback.  As Fig.~\ref{fig:ResVaryVis}.b shows, the levels of feedback arranged by increasing completion time are [mean, mean + variance, full-state, convex-hull].  All experiments lasting over 300s were removed, under the assumption that the user stopped playing. 
Using ANOVA analysis, we rejected the null hypothesis that all visualization methods are equivalent, with $p$-value $2.69\times10^{-19}$.
Anecdotal evidence from beta-testers who played the game suggests that tracking 100 particles is overwhelming---similar to schooling phenomenons that confuse predators---while working with just the mean + variance is like using a ``spongy'' manipulator. Our beta-testers described convex-hull feedback as confusing and irritating.  A single particle left behind an obstacle will stretch the entire hull, obscuring the majority of the swarm.
%obscuring what the rest of the swarm is doing.

>>>>

We designed six experiments to investigate human control of large swarms for manipulation tasks.  Screenshots of representative experiment are shown in Fig.~\ref{fig:5experiments}.  Each experiment examined the effects of varying a single parameter: population of particles for manipulation, four levels of visual feedback, different levels of Brownian noise.%, position control with 1 to 10 particles, and three control architectures for both assembly and foraging tasks. 
 The users could choose which experiment to try, and our architecture randomly assigned a parameter value for each trial.  We recorded the completion time and the participant ID for each successful trial.  
%As Fig.~\ref{fig:Learning} shows, one-third of all participants played only a single game.  Still, many played multiple games, and their decreasing completion times demonstrates their skills improved.

@@

%Transport of goods and materials between points is at the heart of all engineering and construction in real-world systems. 
This experiment varied from 1 to 500 the population of particles used to transport an object. The total area, maximum particle speed, and total net force the swarm could produce were constant. The particles pushed a large hexagonal object through an  {\sffamily S}-shaped maze. We hypothesized participants would complete the task faster with more particles. The results, shown in Fig.~\ref{fig:ResVaryNu}, do not support our hypothesis, indicating a minimum around 130 particles, but only a gradual increase in completion time from 50 to 500.

@@

Our hypothesis predicted a steady decay in performance as the amount of visual feedback decreased.
Our experiment indicated the opposite: players with just the mean completed the task faster than those with full-state feedback.  As Fig.~\ref{fig:ResVaryVis}.b shows, the levels of feedback arranged by increasing completion time are [mean, mean + variance, full-state, convex-hull].  All experiments lasting over 300s were removed, under the assumption that the user stopped playing. 
Using ANOVA analysis, we rejected the null hypothesis that all visualization methods are equivalent, with $p$-value $2.69\times10^{-19}$.
Anecdotal evidence from beta-testers who played the game suggests that tracking 100 particles is overwhelming---similar to schooling phenomenons that confuse predators---while working with just the mean + variance is like using a ``spongy'' manipulator. Our beta-testers described convex-hull feedback as confusing and irritating.  A single particle left behind an obstacle will stretch the entire hull, obscuring the majority of the swarm. Similarly, our algorithm must be robust to outliers.
%obscuring what the rest of the swarm is doing.

### 2017-04-27 journalSwarmControl/experiment.tex
All the comments are solved.

This section analyzes an \emph{object manipulation} task attempted by our hybrid, hysteresis-based controllers.%, inspired by the analysis of human users in \S \ref{sec:expResults}.  
  The swarm must deliver the object to the goal region.  To solve this object manipulation task we divide the task into three components: 1) designing a policy for the object, 2) pushing the object with a compliant swarm, and 3) managing outliers.
\subsection{Learning a policy for the object}\label{subsec:objectpolicy}

To design the policy we first discretize the environment. 
In \cite{ShahrokhiIROS2015}, we used breadth-first search (BFS) on this discretized grid,% to determine $\mathbf{M}_{BFS}$, the shortest distance from any grid cell to the goal, and generated a gradient map $\nabla \mathbf{M}$  shown in Fig.~\ref{fig:BFSGradient}.  
%The object's center of mass is at $\mathbf{b}$ and has average radius $r_b$, so we define the desired direction for the object as $\mathbf{D}(\mathbf{b}) = \nabla \mathbf{M}(\mathbf{b})$. 
%The robots were directed behind the object at  $\mathbf{b} - 1.5 r_b \mathbf{D}(\mathbf{b})$, then directed to  $\mathbf{b} - 0.1 r_b \mathbf{D}(\mathbf{b})$ to push the object toward the goal location. 
but using workspace BFS fails to account for the hull of the object and will suggest moves that can cause collisions with the workspace. A configuration-space BFS approach avoids that problem but still fails to model uncertain actuation of the object by the swarm.

@@

% A corresponding reward function gives a high reward to the goal state,  
% a large negative reward to states including obstacles, and a small negative reward to all other states.
The reward function $r(x,\mathbf{u})$ is defined as
\begin{align}
r(x,\mathbf{u}) &=  \left\{
\begin{array}{ll}
     +100, &  \textrm{if } \mathbf{u} \textrm{ leads to goal state}\\
      -100, & \textrm{if } \mathbf{u} \textrm{ leads to a state with an obstacle} \\
      -1, & \textrm{otherwise}\\
\end{array} 
\right.
\end{align}
 where $\mathbf{u}$ is the action and $x$ is the current state.   %cumulative expected
  Value iteration computes $\hat{V}(x)$, the expected discounted sum reward if the optimal policy is implemented, for the object starting in each state $x$. The optimal policy is %the control action that, in probability, results in the largest value:
   \begin{align} \mathbf{D}(x) = \arg\max_{\mathbf{u}}   [ r(x,\mathbf{u}) + \sum\limits_{j=1}^N \hat{V}(x_j) p(x_j|x, \mathbf{u})].  \label{eq:OptimalPolicy}
   \end{align}
   The value function $\hat{V}(x_j) $ is calculated by computing the value $\hat{V}$ for all $N$ states and iterating until convergence:
\begin{align}
\text{for }&\text{$i=1$ to $N$ do} \nonumber \\
&\hat{V} (x_j) = \gamma \max_{\mathbf{u}} [r(x_j,\mathbf{u}) + \sum\limits_{i=1}^N \hat{V}(x_i) p(x_i| x_j,\mathbf{u})] \label{eq:ValueIteration} \nonumber\\
\text{end}& 
\end{align}
In our experiments $\gamma = 0.97$, and \eqref{eq:ValueIteration} was iterated 200 times. A {\sc Matlab} implementation of this algorithm is available at \cite{Becker2015MDP}.
%Rather than a shortest distance to goal, $\nabla \mathbf{M}_{MDP}$  gives the approximate minimum cost to goal.

$\mathbf{M}_{BFS}$ and the value function are shown in Fig.~\ref{fig:BFSGradient}. 
In 10 simulations with 100 robots, pushing the object to goal using BFS required 183$\pm$179 s while Policy Iteration required 90$\pm$35 s (mean$\pm$std).
%\todo{(report results of 10 simulations with BFS and with PI.  Give mean and std)}

@@

In 10 simulations with 100 robots, pushing the object to goal without a repulsive potential field failed in two of twelve runs. No failures occurred with the repulsive potential field.  Of successful trials, completion time without repulsive potential fields required 245$\pm$135 s while using repulsive potential fields required 90$\pm$35 s (mean$\pm$std).
%In 10 simulations with 100 robots, completion time without repulsive potential fields required $\mu=245, \sigma=135$s while using repulsive potential fields required $\mu=90, \sigma=35$.

@@

The variance controller in Alg.~\ref{alg:MeanVarianceControl} is a greedy algorithm that is susceptible to outliers. 
The controller in \cite{ShahrokhiIROS2015} failed in $14\%$ trials, some particles were unable to reach the object because workspace obstacles were blocking them. This failure rate increases if  object weight increases or ground-robot friction increases. The mean and covariance calculations \eqref{eq:meanVar} included all robots in the workspace. Robots that cannot reach the object due to obstacles skew these calculations. The state machine in Fig.\ \ref{fig:Region}a solves this problem by creating two states for the maze: either main or transfer. Each state has a set of regions representing a discretized visibility polygon. Whenever the object crosses a region boundary the state toggles. The main regions are generated by extending obstacles until they meet another obstacle. The transfer regions are perpendicular to obstacle boundaries, and act as a buffer between two main regions.

@@

In 10 simulations with 100 robots, completion time without outlier rejection required 245$\pm$135 s while using outlier rejection required 90$\pm$35 s (mean$\pm$std).
%\todo{report results of 10 simulations with and without regions.  Give mean and std}

@@

\subsection{Simulation results}\label{sec:AlgObjectManipulation}
 We use the hybrid hysteresis-based controller in Alg.~\ref{alg:MeanVarianceControl}  to track the desired position, while maintaining sufficient robot density to move the object by switching to minimize variance whenever variance exceeds a set limit:  $0.003 W$ and $0.006 W$ were added to the min and max variance limits from \eqref{eq:sigMaxMin}.
 The minimize variance control law \eqref{eq:PDcontrolVariance} is slightly modified to choose the nearest corner further from the goal than $\mathbf{b}$ with an obstacle-free straight-line path to $\mathbf{b}$. 
The control algorithm  for object manipulation is listed in Alg.~\ref{alg:BlockPushing}.

@@

\begin{algorithm}
\caption{Object-manipulation controller for a robotic swarm.}\label{alg:BlockPushing}
\begin{algorithmic}[1]
\Require Knowledge of moveable object's center of mass $\mathbf{b}$; swarm mean $[\bar{x},\bar{y}]$ and variance $[\sigma_x^2, \sigma_y^2]$, each calculated using the regions function from \S \ref{subsec:OutlierRejection};  map of the environment
\State Compute optimal policy for object, according to \S \ref{subsec:objectpolicy}
\While{$\mathbf{b}$ is not in goal region}
\State $\sigma^2 \gets \max{(\sigma_x,\sigma_y)}$
\If {$\sigma^2 > \sigma_{max}^2$}
\While{$\sigma^2 > \sigma_{min}^2$}
\State $ [x_{goal}, y_{goal}] \gets $ nearest corner in region
\State Apply \eqref{eq:PDcontrolPosition} to move toward $[x_{goal}, y_{goal}]$
\EndWhile
\Else  
%\If {$\mathrm{distance}( \mathbf{b}, [x_{goal}, y_{goal}] ) > k_1 r_b$}
%	\State$r_p \gets k_2 r_b$  \Comment{guarded move}
%	\Else
%	\State$r_p \gets k_3 r_b$  \Comment{pushing move}
%	\EndIf
%\State$r_p \gets k_3 r_b$  \Comment{pushing move}
\State Calculate $\mathbf{D}(\mathbf{b})$  \Comment{direction for object at $\mathbf{b}$}
\State Apply \eqref{eq:potentialfield}   \Comment{potential field for swarm}
\EndIf
\EndWhile
\end{algorithmic}
\end{algorithm}

>>>>

This section analyzes an \emph{object manipulation} task attempted by our hybrid, hysteresis-based controllers. The swarm must deliver the object to the goal region.  To solve this object manipulation task we divide the task into three components: 1) designing a policy for the object, 2) pushing the object with a compliant swarm, and 3) managing outliers.
\subsection{Learning a policy for the object}\label{subsec:objectpolicy}

To design the policy we first discretize the environment. 
In \cite{ShahrokhiIROS2015}, we used breadth-first search (BFS) on this discretized grid, but using workspace BFS fails to account for the hull of the object and will suggest moves that can cause collisions with the workspace. A configuration-space BFS approach avoids that problem but still fails to model uncertain actuation of the object by the swarm.

@@

% A corresponding reward function gives a high reward to the goal state,  
% a large negative reward to states including obstacles, and a small negative reward to all other states.
The reward function $r(x,\mathbf{u})$ is defined as
\begin{align}
r(x,\mathbf{u}) &=  \left\{
\begin{array}{ll}
     +100, &  \textrm{if } \mathbf{u} \textrm{ leads to goal state}\\
      -100, & \textrm{if } \mathbf{u} \textrm{ leads to an obstacle state} \\
      -1, & \textrm{otherwise}\\
\end{array} 
\right.
\end{align}
 where $x$ is the current state and $\mathbf{u}$ is the action.   %cumulative expected
  Value iteration computes $\hat{V}(x)$, the expected discounted sum reward if the optimal policy is implemented, for the object starting in each state $x$. The optimal policy is %the control action that, in probability, results in the largest value:
   \begin{align} \mathbf{D}(x) = \arg\max_{\mathbf{u}}   [ r(x,\mathbf{u}) + \sum\limits_{j=1}^N \hat{V}(x_j) p(x_j|x, \mathbf{u})].  \label{eq:OptimalPolicy}
   \end{align}
   The value function $\hat{V}(x_j) $ is calculated by computing the value $\hat{V}$ for all $N$ states and iterating until convergence:
\begin{align}
\text{for }&\text{$i=1$ to $N$ do} \nonumber \\
&\hat{V} (x_j) = \gamma \max_{\mathbf{u}} [r(x_j,\mathbf{u}) + \sum\limits_{i=1}^N \hat{V}(x_i) p(x_i| x_j,\mathbf{u})] \label{eq:ValueIteration} \nonumber\\
\text{end}& 
\end{align}
In our experiments $\gamma = 0.97$, and \eqref{eq:ValueIteration} was iterated 200 times. A {\sc Matlab} implementation of this algorithm is available at \cite{Becker2015MDP}.
%Rather than a shortest distance to goal, $\nabla \mathbf{M}_{MDP}$  gives the approximate minimum cost to goal.

$\mathbf{M}_{BFS}$ and the value function are shown in Fig.~\ref{fig:BFSGradient}. 
In 10 simulations with 100 particles, pushing the object to goal using BFS required 183$\pm$179 s while Policy Iteration required 90$\pm$35 s (mean$\pm$std).
%\todo{(report results of 10 simulations with BFS and with PI.  Give mean and std)}

@@

In 10 simulations with 100 particles, pushing the object to goal without a repulsive potential field failed in two of twelve runs. No failures occurred with the repulsive potential field.  Of successful trials, completion time without repulsive potential fields required 245$\pm$135 s while using repulsive potential fields required 90$\pm$35 s (mean$\pm$std).
%In 10 simulations with 100 robots, completion time without repulsive potential fields required $\mu=245, \sigma=135$s while using repulsive potential fields required $\mu=90, \sigma=35$.

@@

The variance controller in Alg.~\ref{alg:MeanVarianceControl} is a greedy algorithm that is susceptible to outliers. 
The controller in \cite{ShahrokhiIROS2015} failed in $14\%$ trials, some particles were unable to reach the object because workspace obstacles were blocking them. This failure rate increases if  object weight increases or ground-robot friction increases. The mean and covariance calculations \eqref{eq:meanVar} included all particles in the workspace. Particles that cannot reach the object due to obstacles skew these calculations. The state machine in Fig. \ref{fig:Region}a solves this problem by creating two states for the maze: either main or transfer. Each state has a set of regions representing a discretized visibility polygon. Whenever the object crosses a region boundary the state toggles. The \emph{main} regions are generated by extending obstacles until they meet another obstacle. The \emph{transfer} regions are perpendicular to obstacle boundaries, and act as a buffer between two main regions.

@@

In 10 simulations with 100 robots, completion time without outlier rejection required 271$\pm$267 s while using outlier rejection required 90$\pm$35 s (mean$\pm$std).
%\todo{report results of 10 simulations with and without regions.  Give mean and std}

@@

\subsection{Simulation results}\label{sec:AlgObjectManipulation}
 We use the hybrid hysteresis-based controller in Alg.~\ref{alg:MeanVarianceControl}  to track the desired position, while maintaining sufficient robot density to move the object by switching to minimize variance whenever variance exceeds a set limit:  $0.003 W$ and $0.006 W$ were added to the min and max variance limits from \eqref{eq:sigMaxMin}.
 The minimize variance control law \eqref{eq:PDcontrolVariance} is slightly modified to choose the nearest corner further from the goal than the object with an obstacle-free straight-line path to the object. 
The control algorithm  for object manipulation is listed in Alg.~\ref{alg:BlockPushing}.

@@

\begin{algorithm}
\caption{Object-manipulation controller for a robotic swarm.}\label{alg:BlockPushing}
\begin{algorithmic}[1]
\Require Knowledge of moveable object's center of mass $\mathbf{b}$; swarm mean $[\bar{x},\bar{y}]$ and variance $[\sigma_x^2, \sigma_y^2]$, each calculated using the regions function from \S \ref{subsec:OutlierRejection};  map of the environment
\State Compute optimal policy for object, according to \S \ref{subsec:objectpolicy}
\While{is not in goal region}
\State $\sigma^2 \gets \max{(\sigma_x,\sigma_y)}$
\If {$\sigma^2 > \sigma_{max}^2$}
\While{$\sigma^2 > \sigma_{min}^2$}
\State $ [x_{goal}, y_{goal}] \gets $ nearest corner in region
\State Apply \eqref{eq:PDcontrolPosition} to move toward $[x_{goal}, y_{goal}]$
\EndWhile
\Else  
%\If {$\mathrm{distance}( \mathbf{b}, [x_{goal}, y_{goal}] ) > k_1 r_b$}
%	\State$r_p \gets k_2 r_b$  \Comment{guarded move}
%	\Else
%	\State$r_p \gets k_3 r_b$  \Comment{pushing move}
%	\EndIf
%\State$r_p \gets k_3 r_b$  \Comment{pushing move}
\State Calculate $\mathbf{D}(\mathbf{b})$  \Comment{direction for object at $\mathbf{b}$}
\State Apply \eqref{eq:potentialfield}   \Comment{potential field for swarm}
\EndIf
\EndWhile
\end{algorithmic}
\end{algorithm}

### 2017-04-27 journalSwarmControl/realExperiment.tex
Changed the swarm control Journal, added code.
All the comments are solved.

The kilobots performed five successful runs manipulating a hexagonal object through an obstacle maze. Videos of these runs are in Extension 2.
Each trial used 100 kilobots. Trials two through five were performed in a row with no failures in between.  For each trial, fully charged kilobots were placed in the lower left-hand of the workspace, as shown in Fig.~\ref{fig:expSnapShot}.  The moveable object was placed in the lower center of the workspace.  {\sc Matlab} code for vision processing, the policy iteration of \S \ref{subsec:objectpolicy} and the algorithm of \S \ref{sec:AlgObjectManipulation} is available on {\sc Matlab} Central by \cite{Shahrokhi2015MDP}.
Trials were run until the object COM entered the goal region.  The trials ran for \{1465, 3457, 3000, 2162, 2707\} s.  This is $2558\pm771$ s (mean$\pm$std).

>>>>

The kilobots performed five successful runs manipulating a hexagonal object through an obstacle maze. Videos of these runs are in Extension 2. These hardware experiments represent the results of over 100 hours of trials.
Each trial used 100 kilobots. Trials two through five were performed in a row with no failures in between.  For each trial, fully charged kilobots were placed in the lower left-hand of the workspace, as shown in Fig.~\ref{fig:expSnapShot}.  The moveable object was placed in the lower center of the workspace.  {\sc Matlab} code for vision processing, the policy iteration of \S \ref{subsec:objectpolicy} and the algorithm of \S \ref{sec:AlgObjectManipulation} is available on {\sc Matlab} Central at \cite{Shahrokhi2015MDP}.
Trials were run until the object COM entered the goal region.  The trials ran for \{1465, 3457, 3000, 2162, 2707\} s.  This is $2558\pm771$ s (mean$\pm$std).

### 2017-04-27 journalSwarmControl/relatedWork.tex
All the comments are solved.

 \paragraph{Sensing---large populations}
$n$ differential-drive robots in a 2D workspace require $3n$ state variables. Even holonomic robots require $2n$ state variables. Numerous methods exist for measuring this state in microrobotics.  These solutions use computer vision systems to sense position and heading angle, with corresponding challenges of handling missed detections and image registration between detections and robots.  These challenges are increased at the nanoscale where sensing competes with control for communication bandwidth.   We examine control when the operator has access to partial feedback, including only the first and/or second moments of a population's position, or only the convex-hull containing the robots.

@@

Several user studies compare methods for controlling large swarms of simulated robots, for example \cite{bashyal2008human,kolling2012towards,de2012controllability}.  These studies provide insights but are limited by cost to small user studies; have a closed-source code base; and focus on controlling intelligent, programmable agents.  
For instance, the studies \cite{bashyal2008human},  \cite{de2012controllability}, and \cite{kolling2012towards}  were limited to a pool of 5, 18, and 32  participants.
	Using an online testing environment, we conduct similar studies but with sample sizes three orders of magnitude larger.

>>>>

 \paragraph{Sensing---large populations}
$n$ differential-drive robots in a 2D workspace require $3n$ state variables. Even holonomic robots require $2n$ state variables. Numerous methods exist for measuring this state in microrobotics \cite{Peyer2013,Chiang2011,martel2014computer}.  These solutions use computer vision systems to sense position and heading angle, with corresponding challenges of handling missed detections and image registration between detections and robots.  These challenges increase at small scales where sensing competes with control for communication bandwidth.   We examine control when the operator has access to partial feedback, including only the first and/or second moments of a population's position, or only the convex-hull containing the robots.

@@

Several user studies compare methods for controlling large swarms of simulated robots, for example \cite{bashyal2008human,de2012controllability,kolling2012towards}.  These studies provide insights but are limited by cost to small user studies; have a closed-source code base; and focus on controlling intelligent, programmable agents.  
For instance, the studies \cite{bashyal2008human},  \cite{de2012controllability}, and \cite{kolling2012towards}  were limited to a pool of 5, 18, and 32  participants.
	Using an online testing environment, we conduct similar studies but with sample sizes three orders of magnitude larger.
